Plots

### 2025-03-31 Archive/Plots.Rmd
Removed no longer needed plots and fixed figure 3

# Figure 3

setup
```{r}
library("gamlss")
library("qqconf")
dhm <- times |>
  filter(Type == "F" | Type == "S") |>
  filter(Gender == "M") |>
  filter(Time != "DNS") |>
  filter(RxnTime > 0) |>
  filter(Event == "100 Dash" | Event == "110 Hurdles")

dhm$Venue <- as.factor(dhm$Venue)
dhm$Heat <- as.factor(dhm$Heat)
gg3b  <- gamlss(RxnTime ~ random(Venue), sigma.formula = ~ random(Heat), data = dhm, family = GG, control = gamlss.control(n.cyc = 40))

dhm_no2022 <- times |>
  filter(Type == "F" | Type == "S") |>
  filter(Gender == "M") |>
  filter(Time != "DNS") |>
  filter(RxnTime > 0) |>
  filter(Event == "100 Dash" | Event == "110 Hurdles") |>
  filter(Venue != 2022) |>
  mutate(Venue = as.factor(Venue), Heat = as.factor(Heat))

gg3b_no2022  <- gamlss(RxnTime ~ random(Venue), sigma.formula = ~ random(Heat), data = dhm_no2022, family = GG, control = gamlss.control(n.cyc = 40))

```

plot 1
```{r}
venue_effects <- as.data.frame(gg3b$mu.coefSmo[[1]]$coef)
colnames(venue_effects) <- c("Effect Value")

venue_plot <- ggplot(venue_effects, aes(x = rownames(venue_effects),
                                               y = `Effect Value`)) +
  geom_point() + 
  labs(x = "Venue", y = "Venue Effect")+
  scale_y_continuous(limits = c(-0.15, 0.1))
```
plot 2
```{r}
venue_effects_no2022 <- as.data.frame(gg3b_no2022$mu.coefSmo[[1]]$coef)
venue_effects_no2022["2022", ] <- 1 #Arbitrary number out of range of y scale so
#that the x axis line up

colnames(venue_effects_no2022) <- c("Effect Value")

venue_plot_no2022 <- ggplot(venue_effects_no2022,
                                   aes(x = rownames(venue_effects_no2022),
                                       y = `Effect Value`)) +
  geom_point() + 
  labs(x = "Venue", y = "Venue Effect") +
  scale_y_continuous(limits = c(-0.15, 0.1))
```
### Now we combine for final product
```{r}
library(gridExtra)
venue_effects_combined <- grid.arrange(venue_plot,
                                       venue_plot_no2022, ncol = 1)
ggsave(filename = "ComparisonOfVenueEffects.pdf", path = "../Manuscript",
       plot=venue_effects_combined, height = 6.5, width = 7)
```

# Figure 4
Calculation of curve
```{r}
simfit <- function(model, n = 10000000) {
    set.seed(1)
    sd_Venue <- model$mu.coefSmo[[1]]$sigb
    sd_Venue_heat <- model$sigma.coefSmo[[1]]$sigb[1]

@@

    rGG(n, mu = mu, sigma = sigma, nu = nu)
}
samplefit <- simfit(gg3b)
samplefit0 <- samplefit[1:1000000]
kernfit <- density(samplefit0)

```

Now we make the density graph
```{r}
make_graph <- function(n = 1000000){
  plot(density(samplefit, n=n), xlim = c(0, 0.3), ylim = c(0, 25), xlab = "",
     main = "")
  curve(dGG(x, mu = exp(gg3b$mu.coefficients[1]),
          sigma = exp(gg3b$sigma.coefficients[1]),
          nu = gg3b$nu.coefficients[1]),0, 0.3, add = TRUE, col = "blue",
      main = "", xlab = "", ylab = "")
}
density_plot <- make_graph(1000000)
```

And combine it with the residuals
```{r}
library(gridExtra)
resid_plot <- qq_conf_plot(residuals(gg3b), dparams = list(mean = 0, sd = 1))
density_plot <- grid.arrange(resid_plot, density_plot, ncol = 2)
ggsave(filename = "ResidualsDensityPlot", path = "../Manuscript",
       plot=resid_density, height = 4, width = 8)
```

>>>>

# Figure 3
setup
```{r}
library(tidyverse)
library("gamlss")
dhm <- times |>
  filter(Type == "F" | Type == "S") |>
  filter(Gender == "M") |>
  filter(Time != "DNS") |>
  filter(RxnTime > 0) |>
  filter(Event == "100 Dash" | Event == "110 Hurdles")
dhm$Venue <- as.factor(dhm$Venue)
dhm$Heat <- as.factor(dhm$Heat)

gg3b <- gamlss(RxnTime ~ random(Venue), sigma.formula = ~ random(Heat), data = dhm, family = GG, control = gamlss.control(n.cyc = 40))

simfit <- function(model, n = 10000000) {
    set.seed(1)
    sd_Venue <- model$mu.coefSmo[[1]]$sigb
    sd_Venue_heat <- model$sigma.coefSmo[[1]]$sigb[1]

@@

    rGG(n, mu = mu, sigma = sigma, nu = nu)
}

samplefit <- simfit(gg3b)
samplefit0 <- samplefit[1:1000000]
```

Generates the plot:
```{r}
library("qqconf")
pdf("../Manuscript/diagnosis.pdf", height=3.25, width = 7, pointsize = 9)
par(mfrow = c(1, 2), mar = c(2.5, 2.5, .1, .1), mgp = c(1.5, 0.5, 0))
hist(dhm$RxnTime, freq=FALSE, breaks=seq(.05, .40, by = .01),
     xlab = "Reaction time", main = "")
kernfit <- density(samplefit0)
lines(kernfit$x, kernfit$y) # /1.434) ## density() seems to have a bug for n too large
## curve(dGG(x, mu = exp(gg0$mu.coefficients[1]),
##           sigma = exp(gg0$sigma.coefficients[1]),
##           nu = gg0$nu.coefficients[1]), add = TRUE, col = "blue")
qq_conf_plot(residuals(gg3b), dparams = list(mean = 0, sd = 1)) ## z-scores have known mean and sd
dev.off()
```
